Supplementary Materials

### 2017-02-15 Report06-12.Rmd
Binary AMIFaces

#parallel coordinate plot, vars on x????
#unpack intercept
#don't force to zero
#convert into full model decription - every single level combination
#have every level and cross level - order combinations by p value
#function for estimates for each treatment
#multinomail 
```

>>>>

#parallel coordinate plot, vars on x????
#unpack intercept
#don't force to zero
#convert into full model decription - every single level combination
#have every level and cross level - order combinations by p value
#function for estimates for each treatment
#multinomail 
#add hit or miss column, to utilise caret package
```

### 2017-02-15 Supplementary Materials.Rmd
Binary AMIFaces

glmFits <- ALLmetaIMGFaces %>%
  split(.$FaceKey) %>%
  map_df(~ hitmiss(.)) %>%
  split(.$type) %>%
  map(~ glm(hit ~ ., data = select(., -type, -file)))

@@

>>>>

glmFits <- ALLmetaIMGFaces %>%
  split(.$FaceKey) %>%
  map_df(~ hitmiss(.)) %>%
  split(.$type) %>%
  map(~ glm(hit ~ 0+., data = select(., -type, -file)))

@@

```{r Caret, fig.cap = "\\label{Caret}"}
library(caret)
library(e1071)
set.seed(100)

ALLmetaIMGFaces
inTrain <- createDataPartition(y = ALLmetaIMG$matchesManual, p = .75, 
                               list = FALSE)

training <- ALLmetaIMG[ inTrain,]
testing <- ALLmetaIMG[-inTrain,]

ctrl <- trainControl(method = "repeatedcv",
repeats = 3,
classProbs = TRUE,
summaryFunction = twoClassSummary)

plsFit <- train(hit ~ .,
 data = training,
 method = "pls",
 ## Center and scale the predictors for the training
 ## set and all future samples.
 preProc = c("center", "scale"), metric="Accuracy")

# plsFit <- train(hit ~ .,
# data = training,
# method = "glm", 
# tuneLength = 15,
# trControl = ctrl,
# metric = "ROC",
# preProc = c("center", "scale"))
plsFit
